---
title: "scfmCrop"
author: "Steve Cumming and Eliot McIntire"
date: "03 April 2018"
output: pdf_document
---

This module creates the initial vegetation and patch age maps for fire regime simulations. The basic user input is a shapefile __studyArea__. Age and vegetation maps __vegMapInit__ and __ageMapInit__ are loaded from the module's __data__ directory unless provided by the user. 

__vegMapInit__ provides the template resolution and projection for the simulation. If additional layers than the age map are desired, they should be processed in the same manner as __ageMapInit__.

There is no velidation that the __studyArea__ is contained within the extent of __vegMapInit__: this should be verified.


## Input data

__vegMapInit__ is the 250m resolution Land Cover Map of Canada 2005 (v1.2), which is classified multispectral imagery from the Modis sensor. 

__ageMapInit__ is a synthetic 1km resolution product. 

The references for these two data products are:

Latifovic, R., Z-L, Zhu, J. Cihlar, C. Giri, I. Olthof, 2004. Land cover mapping of North and Central America –
Global Land Cover 2000. Remote Sensing of Environment. 89:116-127. The on-line reference is __ftp:\ccrs.nrcan.gc.ca\AD\EMS\Landcover2005__.

Pan, Y., Chen, J. M., Birdsey, R., McCullough, K., He, L., & Deng, F. (2011). Age structure and disturbance legacy of North American forests. Biogeosciences 8(3): 715-732. doi:10.5194/bg-8-715-2011.

## Output data

__vegMap__ cropped and masked to __studyArea__
__ageMap__ reprojected to the projection and resolution and extent of __vegMap__, with the equivalent mask.
__Mask__ derived from __vagMap__, values 1 or __NA__ depending on cell's being within the __studyArea__ or not. 

The following code chunk loads and plots a specifed polygon from the Ecoregion shapefile, obtained onoine from NRCAN.


```{r loadShp, echo=FALSE}
library(rgdal)
library(SpaDES)
library(magrittr)
dev.off()
dev(4)
newPlot()
dataDir<-file.path("data", "Ecoregions")
shape <- readOGR(dsn = dataDir, layer = "ecoregions")
Plot(shape)
studyArea<-shape[shape$ECOREGION==87,] #we have chosen Athabasca Plains in northern SK
                                       #we happen to know the numeric code is 87 (easier to type)
print(paste("class(studyArea) =",class(studyArea)))
Plot(studyArea)
```

The following code chunk will create the cropped maps in simlist mySim. The two resultant maps are plotted. 

```{r module_usage, message=FALSE}
#Make sure to setwd to project directory
try(rm(mySim))
inputDir <- file.path(tempdir(), "inputs") %>% checkPath(create = TRUE)
outputDir <- file.path(tempdir(), "outputs")
times <- list(start = 0, end = 10)
parameters <- list(
 scfmCrop <- list(
   .useCache = TRUE
 )
)

modules <- list("scfmCrop")
objects <- list(studyArea=studyArea)

paths <- list(
  cachePath = file.path(outputDir, "cache"),
  modulePath = file.path("scfmModules"),
  inputPath = inputDir,
  outputPath = outputDir
)

dev.off()
dev(4)
newPlot()
mySim <- simInit(times = times, params = parameters, modules = modules,
                 objects = objects, paths = paths)
Plot(mySim$vegMap, mySim$ageMap)
tmp <- spades(mySim,debug=FALSE)
```


