---
title: "scfmRegime"
author: "Steve Cumming"
date: "03 August 2015"
output: pdf_document
---


```{r setup, include=TRUE, echo=FALSE, messages=FALSE, results=}
library(SpaDES)
library(magrittr)
library(raster)
knitr::opts_chunk$set(echo = TRUE)
```

This module estimates some fire regime parameters from empirical data.



## Plotting

Nothing.

## Saving

Nothing

## Input data

## Study area

A shapefile is required

## Landscape Attributes

## Fire Points Database

```{r}
# Points
#ftp://ftp.nofc.cfs.nrcan.gc.ca/pub/fire/nfdb/fire_pnt/current_version/NFDB_point.zip
```

## Output data

A list names __scfmPars__ containing the following elements

ignitionRate=rate,
                       pEscape=pEscape,
                       xBar=xBar,       # mean fire size ## SHOULD USE Expected Value?
                       emfs=maxFireSiz

## Anticipated linkages to other modules



First, let's show how to load a shapefile

```{r loadShp, echo=FALSE}
library(rgdal)
library(SpaDES)
library(magrittr)
dev.off()
dev(4)
newPlot()
dataDir<-file.path("data", "Ecoregions")
shape <- readOGR(dsn = dataDir, layer = "ecoregions")
Plot(shape)
studyArea<-shape[shape$ECOREGION==87,] #we have chosen Athabasca Plains in northern SK
                                       #we happen to know the numeric code is 87 (easier to type)
print(paste("class(studyArea) =",class(studyArea)))
Plot(studyArea)
```

Now we can test the fire regime estimatorm and its GIS operations, and thr Caching of the database.

```{r module_usage, message=FALSE}
try(rm(mySim))
inputDir <- file.path(tempdir(), "inputs") %>% checkPath(create = TRUE)
outputDir <- file.path(tempdir(), "outputs")
times <- list(start = 0, end = 10)
parameters <- list(
 scfmRegime <- list(
   .useCache = TRUE,
   fireCause = "L",
   fireEpoch = c(1987,2016)
 )
)

modules <- list("scfmRegime")
objects <- list(studyArea=studyArea,landscapeAttr=list(cellSize=1,burnyArea=1e5))

paths <- list(
  cachePath = file.path(outputDir, "cache"),
  modulePath = file.path("scfmModules"),
  inputPath = inputDir,
  outputPath = outputDir
)

mySim <- simInit(times = times, params = parameters, modules = modules,
                 objects = objects, paths = paths)
tmp <- spades(mySim,debug=FALSE)
```

#